---
title: "Lord of the Rings"
author: "Dr Connor Smith"
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2
bibliography: lotr_refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(forcats)
library(knitr)
```

# Data

The following data was downloaded from Jennifer Bryan of GitHub from <https://github.com/jennybc/lotr-tidy>

```{r load_data, echo=FALSE}
lotr <- read.delim("lotr_clean.tsv")

lotr <- lotr %>% 
  mutate(Film = factor(Film)) 

levels(lotr$Film) <- c("The Fellowship Of The Ring", "The Two Towers", "The Return Of The King")

# Fill the following information in
# options: Bilbo, Frodo, Gandalf, Aragorn, Saruman, Lurtz
fav_char <- "Lurtz"
```

# Favourite Character

In the Lord of the Rings, my favourite character is `r fav_char`. We can check how many words `r fav_char` spoke during the movie with the folololololowing code:

```{r ugly_code}
lotr_fav<-lotr%>%filter(Character == fav_char) %>%summarise(Total_Words = sum(Words))
```

I'm not sure this is correct but it seems that `r fav_char` only spoke `r lotr_fav` words in the entire movie.

# Figure

```{r figure, fig.cap = "Lord of the Rings Movies", fig.height = 5}
lotr %>% 
  group_by(Chapter) %>% 
  summarise(Words = sum(Words), Film = first(Film)) %>%
  ggplot(aes(x = fct_inorder(Chapter), y = Words)) +
  geom_point(aes(colour = Film)) +
  theme(axis.text.x = element_blank()) + 
  facet_grid(~ fct_inorder(Film)) + 
  xlab(label = "Movie Chapters") + 
  ylab(label = "Words Spoken") + 
  ggtitle("Words spoken in LotR movies")
```

Figure \@ref(fig:figure) shows ...

# Table

```{r table}
lotr %>% 
  group_by(Film) %>% 
  summarise(Words = sum(Words)) %>% 
  kable(caption = "Lord of the Rings Movies")
```

# Comments

Lord of the Rings, Star Wars, and participatory fandom: Mapping new congruencies between the internet and media entertainment culture written by @shefrin2004lord is an interesting article.

# References
